Fitness Cost

### 2022-01-25 graphs_newt_snakes/Are_we_at_steadystate.Rmd
I am running cost1on1 for very long periods of time and am prining out the values. I want to see what happens when i change interaction rate and population size. Does a population go extinct? is ther coexistance or coevo? I am also writing and making more graphs in the rmarkdowns

I have noticed that there seems to be no more variation in the populations. On SLiM all of the individuals in their respective populations have the same color indicating same phenotype

>>>>

I have noticed that there seems to be no more variation in the populations. On SLiM all of the individuals in their respective populations have the same color indicating same phenotype. The beta values are all 0's. All of the phenotypes have gotten really small (very close to 0). There is no longer co-evolution, but maybe coexistence.

More things that I have noticed: If interaction rate is higher like 0.15 or 0.10 then one of the populations will go extinct. This might change if the population size is larger

### 2022-01-25 graphs_newt_snakes/fitness_cost.Rmd
I am running cost1on1 for very long periods of time and am prining out the values. I want to see what happens when i change interaction rate and population size. Does a population go extinct? is ther coexistance or coevo? I am also writing and making more graphs in the rmarkdowns

phenotype <- c(0:5)
plot(phenotype, phenotype^2, type = "l", main="Fitness Cost", xlab="Phenotype", ylab="Cost")
abline(v=3, col="red")
abline(h=9, col="red") # represents half of the individuals fitness
```

@@

>>>>

phenotype <- c(0:5)
plot(phenotype, phenotype^2, type = "l", main="Fitness Cost", xlab="Phenotype", ylab="Cost")
abline(v=3, col="red")
abline(h=9, col="red") # represents half of the individuals fitness

@@

```{r, is this pheno what I expect}
phenotype <- c(0:200)
plot(phenotype,exp(-(phenotype/200)^2), type = "l", main="Fitness Cost", xlab="Phenotype", ylab="Cost")
lines(phenotype,exp(-(phenotype/150)^2))
lines(phenotype,exp(-(phenotype/100)^2))
lines(phenotype,exp(-(phenotype/50)^2))
lines(phenotype,exp(-(phenotype/10)^2))
```
